Supplementary Information

### 2021-02-19 doc/manuscript/ForestGEO_treerings_SI.Rmd
Update ForestGEO_treerings_SI.Rmd

$$DBH_Y  = DBH_{m} - 2*\left[r_{bark,m} - r_{bark,Y} + \sum_{y=Y}^{m} RW_{y} \right]$$
Here, $r_{bark}$ denotes bark thickness, which was estimated on a species-specific basis from allometries (Tables `r species_table`, `r bark_allometries`).
If $DBH_m$ was taken before coring, $RW$ values between $y=m$ and $y=Y$ were added instead of subtracted.
If $DBH_m$ was taken after coring, ***...(check code)**

@@

>>>>

$$DBH_Y  = DBH_{m} - 2*\left[r_{bark,m} - r_{bark,Y} + \sum_{y=Y}^{m} RW_{y} \right]$$
Here, $r_{bark}$ denotes bark thickness, which was estimated on a species-specific basis from allometries (Tables `r species_table`, `r bark_allometries`).
If $DBH_m$ was taken before coring, $RW$ values between $y=m$ and $y=Y$ were added instead of subtracted.
If $DBH_m$ was taken $\le$ 10 years after the last year of measurement in the core, we used the equation above, assuming that the $n$ missing measurements between the year of the last $RW$ record in the core and year $m$ were equal to the last $n$ records in the core.

@@

For trees on which a measurement of $DBH_m$ was not available and the distance to pith could be reliably estimated for any cores, $DBH$ could not be reconstructed.
These trees were excluded from all analyses including $DBH$ as an independent variable.
